TBD

### 2021-02-21 outputs/paper/paper.Rmd
Add function to format table for Chi-squared test

```{r, echo = FALSE, include=FALSE, message = FALSE}
#### Global Functions ####
percent <- function(x, decimal = 2, format = "f") {   
  paste0(formatC(x, format = format, digits = decimal), "%")
}
```

@@

q14_chi <- table(all_simulated_dataset$Q14, all_simulated_dataset$type)
chisq.test(q14_chi)
```

>>>>

```{r, echo = FALSE, include=FALSE, message = FALSE}
#### Global Functions ####

### Format percent
percent <- function(x, decimal = 2, format = "f") {   
  paste0(formatC(x, format = format, digits = decimal), "%")
}

### Format table for Chi-squared test
tableChisq <- function(stat, df, p) {   
  chi_stat <- c(stat)
  chi_param <- c(df)
  chi_p <- c(p)
  chi_df <- data.frame(chi_stat, chi_param, chi_p)

  kable(chi_df,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    kable_paper(c("striped", "hover"))
}

@@

### Chi-squared test
q14_chi <- table(all_simulated_dataset$Q14, all_simulated_dataset$type) %>%
  chisq.test()

tableChisq(q14_chi$statistic, q14_chi$parameter, q14_chi$p.value)
```
